---
title: "chpt3.p8"
author: "Claudius Taylor"
date: "7/17/2019"
output: pdf_document
---

```{r results='asis', echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(lubridate)
library(data.table)
library(dplyr)
library(stats)
library(ISLR)
```     

## (a) Use the lm() function to perform a simple linear regression with "mpg" as the response and "horsepower" as the predictor. Use the summary() function to print the results.  
```{r}
data(Auto)
fit <- lm(mpg ~ horsepower, data = Auto)
summary(fit)
```

## How strong is the relationship between the predictor and the response ?
## $R^2$ is equal to 0.6059, almost 61% of the variability in "mpg" can be explained using "horsepower".

## Is the relationship between the predictor and the response +ve or -ve ?
## Since coeficient of "horsepower" is negative, the relationship is also negative.

## (b) What is the predicted $mpg$ associated with a "horsepower" of 98 ? What are the associated 95% confidence and prediction intervals ?
```{r}
predict(fit, data.frame(horsepower = 98), interval = "confidence")
```

## (c) Plot the response and the predictor. Use the abline() function to display the least squares regression line.
```{r}
plot(Auto$horsepower, Auto$mpg, main = "Response vs. Predictor", 
     xlab = "horsepower", ylab = "mpg", col = "blue")
abline(fit, col = "red")
```

## (d) Use the plot() function to produce diagnostic plots of the least squares regression fit. Comment on any problems you see with the fit.
```{r}
par(mfrow = c(2, 2))
plot(fit)
```

## The plot of residuals versus fitted values indicates the presence of nonlinearity in the data. The plot of standardized residuals versus leverage indicates the presence of a few outliers (higher than 2 or lower than -2) and a few high leverage points.